\documentclass[twocolumn,superscriptaddress,aps]{revtex4-1}

\usepackage[utf8]{inputenc}

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}

\usepackage{bbold}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{color}
\usepackage{hyperref}

\begin{document}


% ==============================================================================

\title{\Large{INFO8010: Report template}}
\vspace{1cm}
\author{\small{\bf Miss Pacman}}
\affiliation{\texttt{miss.pacman@student.uliege.be} (\texttt{sXXXXXX})}
\author{\small{\bf Mr Pacman}}
\affiliation{\texttt{mr.pacman@student.uliege.be} (\texttt{sYYYYYY})}

\maketitle

% ==============================================================================

\section{Introduction}
This paper present a method to address the long-standing problem of view synthesis.  View synthesis aims of create any new kind of view from any direction,
given a set of input images along with its known camera poses, of a given scene. NeRF, \textit{ Representing Scenes as Neural Radiance Fields for View Synthesis}, achieves state of the art result by representing a scene using a fully-connected deep neural network that given a viewing direction ($\theta, \phi)$ and a spacial location$(x, y, z)$ outputs an immited color $c=(r,g,b)$ and a volume density $\sigma$.


More intuitivly to represent a pixel 
\bigskip
the radiance emmitted in each direction ($\theta, \phi$) at each point ($x, y, z$) in space. And output a single volume density 
\bigskip

The idea is to overfit a neural network to a particular scene for wh
\bigskip
NeRF, Representing Scenes as Neural Radiance Fields for View Synthesis, represent a scene using a fully-connected deep neural network whose input is a 


is a method that achieves state-of-the-art result of view synthesis. Given a set of input images with known camera poses of a given scene, this method can synthesize any kind of view from any point of view and for any viewing direction, by \textbf{optimizing an underlying continuous volumetric scene function}. Overfit NN to single data point

Formally a scene can 

a neural network fit to a particular scene (overfit a single nn for a particular scene)


Position + viewing direction => Output a color c (what color is at that particular location + density is there something or not). Ask the neural network (that represent the scene, overfit well), in a particular location viewed from a particular angle what am i going to see


Use of fully connected
\section{Section 2}


\section{Section 3}

Donec tempus, neque id maximus mattis, massa est tincidunt augue, vel aliquam felis libero sit amet velit. Mauris id tincidunt leo. Vestibulum iaculis nunc sit amet enim iaculis ornare. Integer et arcu dapibus, tempus tortor eget, porta felis. Aenean iaculis dolor a leo hendrerit sodales. Aenean non odio ligula. Nullam tristique porttitor risus, nec auctor felis pellentesque at. Aenean augue quam, condimentum eu velit quis, tincidunt scelerisque nisi. Mauris maximus lectus a nisl vestibulum, et pretium nulla blandit. Praesent venenatis sit amet felis ac convallis. Donec suscipit hendrerit neque, a gravida arcu sagittis ac. Ut tellus massa, porttitor vel egestas eu, posuere non lacus.

Nunc ac augue auctor, fermentum nisl non, porta nibh. Sed et lobortis felis. Integer purus nibh, fermentum sit amet molestie a, viverra eget tortor. In malesuada finibus bibendum. Etiam sed turpis et eros mollis semper. Phasellus faucibus, tellus ut suscipit ullamcorper, lacus lectus condimentum ipsum, at lacinia dui elit vel lectus. Pellentesque consectetur, lorem sit amet auctor pulvinar, purus tellus ornare nisi, ut consequat velit risus nec dolor. Proin sed sollicitudin purus. Mauris aliquam nisl fermentum lacus rutrum tempor. Vestibulum auctor enim eget eros venenatis, vel auctor metus feugiat. Suspendisse venenatis eu purus ac lobortis.

Donec tempus, neque id maximus mattis, massa est tincidunt augue, vel aliquam felis libero sit amet velit. Mauris id tincidunt leo. Vestibulum iaculis nunc sit amet enim iaculis ornare. Integer et arcu dapibus, tempus tortor eget, porta felis. Aenean iaculis dolor a leo hendrerit sodales. Aenean non odio ligula. Nullam tristique porttitor risus, nec auctor felis pellentesque at. Aenean augue quam, condimentum eu velit quis, tincidunt scelerisque nisi. Mauris maximus lectus a nisl vestibulum, et pretium nulla blandit. Praesent venenatis sit amet felis ac convallis. Donec suscipit hendrerit neque, a gravida arcu sagittis ac. Ut tellus massa, porttitor vel egestas eu, posuere non lacus.


% ==============================================================================
Note need to store a mesh of voxel grid of some scene but a neural network that can be querryed
\bibliographystyle{unsrt}
\bibliography{bibliography.bib}

\end{document}
